Concurrent Programming with CXL

### 2020-06-06 book/paper.tex
Added more challenges

It's not easy.  It would be easy to come up with a solution that uses a single lock
and busy waiting, but we would like to avoid busy waiting.
Introduced by Dijkstra,
a \emph{semaphore} is a primitive that fits the bill.  A semaphore is essentially
a counter that can be incremented and decremented but is not allowed to go
below zero.  The semaphore counter is typically initialized to the number of
units of a resource initially available.
When allocating a resource, a process decrements the
counter using the \texttt{procure} or simply \texttt{P} operation.  The
\texttt{procure} operation blocks the invoking process if the counter is zero.
To release the resource, a process increments the resource using the
\texttt{vacate} or {V} operation.

Figure~\ref{fig:semaphore} shows the \texttt{synch} module implementation of
semaphores.
Figure~\ref{fig:dinerssema} shows a solution to the Italian Philosphers problem
using a semaphore.
One can think of a semaphore as a generalization of a lock.  In fact, a
lock can be implemented by a semaphore initialized to 1.  Then \texttt{P}
acquires the lock, and \texttt{V} releases the lock.

@@

Note the quite different usage of the \texttt{l\_} semaphores and \texttt{n\_}
semaphores.
People often call semaphores that are used as locks \emph{binary semaphores},
as their counters only take on the values 0 and 1.
They protect critical sections.
The second type of semaphores are called \emph{counting semaphores}.
They are essentially used to send signals between processes.
However, binary and counting semaphores are implemented the same way.

>>>>

It's not easy.  It would be easy to come up with a solution that uses a single lock
and busy waiting, but we would like to avoid busy waiting.
Introduced by Dijkstra,
a \emph{semaphore} is a synchronization primitive that fits the bill.
A semaphore is essentially
a counter that can be incremented and decremented but is not allowed to go
below zero.  The semaphore counter is typically initialized to the number of
units of a resource initially available.
When allocating a resource, a process decrements the
counter using the \texttt{procure} or simply \texttt{P} operation.  The
\texttt{procure} operation blocks the invoking process if the counter is zero.
To release the resource, a process increments the resource using the
\texttt{vacate} or {V} operation.

Figure~\ref{fig:semaphore} shows the \texttt{synch} module implementation of
semaphores.
Figure~\ref{fig:dinerssema} shows a solution to the Italian Philosphers problem
using a semaphore.

\begin{quote}
\begin{itemize}
\item Can you come up with a test (an assertion) that shows that at most three
philosophers are eating at the same time?
\item Can you come up with a test (different code) that checks to see that
the solution allows more than one philosopher to eat at the same time?
\end{itemize}
\end{quote}

One can think of a semaphore as a generalization of a lock.  In fact, a
lock can be implemented by a semaphore initialized to 1.  Then \texttt{P}
acquires the lock, and \texttt{V} releases the lock.

@@

Note the quite different usage of the \texttt{l\_} semaphores and \texttt{n\_}
semaphores.
People often call semaphores that are used as locks \emph{binary semaphores},
as their counters only take on the values 0 and 1.
They protect critical sections.
The second type of semaphores are called \emph{counting semaphores}.
They can be used to send signals between processes.
However, binary and counting semaphores are implemented the same way.
